Classless Java

### 2016-03-24 OOPSLA16/sections/CaseStudy.tex
13pages

\vspace{0.5em}
\begin{tabular}{llll}
\hline
\rowcolor[HTML]{C0C0C0} 
Code               & SLOC & Code               & SLOC \\ \hline
old (\texttt{eval})         & 626  & new (\texttt{eval})         & 560  \\ 
\rowcolor[HTML]{C0C0C0}
old (\texttt{eval} + \texttt{print}) & 661  & new (\texttt{eval} + \texttt{print}) & 677  \\ \hline
\end{tabular}

>>>>

\vspace{0.5em}
\begin{tabular}{cccc}
\hline
\rowcolor[HTML]{C0C0C0} 
Code               & SLOC & Code               & SLOC \\ \hline
old (\texttt{eval})         & 626  & old (\texttt{eval} + \texttt{print}) & 661  \\ 
\rowcolor[HTML]{C0C0C0}
new (\texttt{eval})         & 560  & new (\texttt{eval} + \texttt{print}) & 677  \\ \hline
\end{tabular}

### 2016-03-24 OOPSLA16/sections/Conclusion.tex
spell and grammar check
13pages

\section{Conclusion}\label{sec:conclusion}

Before Java 8, concrete methods and static methods were not allowed
to appear in interfaces.  Java 8 allows static interface methods and
introduces \emph{default methods}, which enables implementations
inside interfaces. This had an important positive consequence that
was probably overlooked: the concept of class
(in Java) is now (almost) redundant and unneeded.
We proposed a programming style, called Classless Java, where
truly \objectoriented programs and (reusable) libraries
can be defined and used without ever defining a single class.

@@

Classless Java is just a programming style, but is showing the way
for a new flavour of object orientation: We propose \interfacebased
\objectoriented languages (IB), as opposed to \classbased or
\prototypebased.  In IB state is not modelled at the platonic/ideal
level but is handled excursively by instances.  This unlocks useful
code reuse patterns, as shown in Section~\ref{sec:ep}.
An interesting avenue for future work would be to design a new
language based on IB. With a proper language design we would not need 
to restrict ourselfves to the limitations of Java and its syntax.

>>>>

\section{Conclusion}\label{sec:conclusion}
Before Java 8, concrete methods and static methods were not allowed
to appear in interfaces.  Java 8 allows static interface methods and
introduces \emph{default methods}, which enables implementations
inside interfaces. This had an important positive consequence that
was probably overlooked: the concept of class
(in Java) is now (almost) redundant and unneeded.
We proposed a programming style, called Classless Java, where
truly \objectoriented programs and (reusable) libraries
can be defined and used without ever defining a single class.

@@

Classless Java is just a programming style, but is showing the way
for a new flavour of object orientation: We propose \interfacebased
\objectoriented languages (IB), as opposed to \classbased or
\prototypebased.  In IB state is not modelled at the platonic/ideal
level but is handled excursively by instances.  This unlocks useful
code reuse patterns, as shown in Section~\ref{sec:ep}.
An interesting avenue for future work would be to design a new
language based on IB. With a proper language design we would not need
to restrict ourselves to the limitations of Java and its syntax.
